---
title: "AIM paper analysis"
author: "Elsie Horne"
date: "22/09/2021"
output:
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include=FALSE, message = FALSE, warning = FALSE)
```

```{r}
dir.create(here::here("output", "report"), showWarnings = FALSE, recursive=TRUE)
```

```{r libraries}
library(tidyverse)
library(glue)
library(readr)
library(flextable)
```

```{r source_functions}
source(here::here("analysis", "lib", "sanitise_variables.R"))
```

```{r flextable_functions}
my_flextable_1 <- function(.data) {
  .data %>%
    flextable() %>%
    fontsize(size=10) %>%
    autofit() %>%
    theme_vanilla()
}

my_flextable_2 <- function(.data) {
  .data %>%
    flextable() %>%
    # add_header_row(values = c("", "OR (95% CI)"), colwidths = c(1,3)) %>%
    fontsize(size=10) %>%
    autofit() %>%
    theme_vanilla()
}
```


## Identification and description of individuals who remain unvaccinated 12 weeks after becoming eligible for vaccination 

### Methods

Inclusion criteria:

- Individuals alive and registered at a single TPP practice for at least 1 year prior to vaccine eligibility date
- Individuals satisfying the criteria for one of the following:
    - JCVI priority group 2 (80-120 years and not in group 1, eligible from 8th December 2020)
    - JCVI priority group 9 (50-54 years and not in groups 1-8, eligible from 19th March 2021)
    - JCVI priority group 11 (30-39 years and not in groups 1-10, eligible from 13th - 26th May 2021)

For individuals in JCVI priority group 11, eligibility date was dependent on age:
```{r elig_dates, include=TRUE}
read_rds(here::here("output", "data", "elig_dates_tibble.rds")) %>%
  my_flextable_1()
```

#### Outcome

- 0 if no record of COVID vaccination up until 12 weeks after eligibility date
- 1 if record of any brand of COVID vaccination any time up until 12 weeks after eligibility date

#### Covariates

The following clinical variables were defined based on definitions given in _COVID-19: the green book, chapter 14a_^[https://assets.publishing.service.gov.uk/government/uploads/system/uploads/attachment_data/file/1018444/Greenbook_chapter_14a_16Sept21.pdf]: severe asthma, chronic respiratory disease, chronic heart disease, chronic kidney disease, chronic liver disease, chronic neurological disease, diabetes (other endocrine disorders), immunosupressed, asplenia/dysfunction of spleen, severe mental illness.

All clinical and demographic covariates were defined based on information up until the individual's eligibility date.

Covariates related to COVID infection were split according to whether they occurred before the eligibility date or in the 12-week period after the eligibility date:

- COVID +ve test before eligible
- COVID +ve test while eligible
- COVID hospitalisation before eligible
- COVID hospitalisation while eligible

Covariates relating to death or deregistration were defined during the 12-week period after the eligibility date:

- Death while eligible (COVID on certificate)
- Death while eligible (COVID +ve within 28 days)
- Death while eligible (any cause)
- Deregistered while eligible

#### Analysis plan

- From the individuals that satisfy the inclusion criteria, and for each eligibility group:
    - identify all unvaccinated individuals (no vaccination within 12 weeks of their eligibility date) 
    - randomly select 10% of the individuals who received a first vaccination within 12 weeks of their eligibility date
- Generate summary table of the characteristics stratified by vaccinated/unvaccinated groups defined above (using inverse probability weights to correct for the random sampling of vaccinated patients)
- Fit logistic regression models for remaining unvaccinated (using inverse probability weights to correct for the random sampling of vaccinated patients) 

### Results

Table 1. Characteristics of individuals in JCVI priority group 2 aged 80+ years. 'Unvaccinated' = patients who did not receive a COVID vaccine within 12 weeks of becoming eligible; 'Vaccinated' otherwise. Age is summarised as mean (SD), all other characteristics are n (%). Inverse probability weights used to correct for the random sampling of 'Vaccinated' patients.
```{r table1, include=TRUE}
read_rds(here::here("output", "tables", str_c("summary_table_02.rds"))) %>%
  my_flextable_1()
```
<!-- \pagebreak -->
Table 2. Characteristics of individuals in JCVI priority group 9 aged 50-54 years. 'Unvaccinated' = patients who did not receive a COVID vaccine within 12 weeks of becoming eligible; 'Vaccinated' otherwise. Age is summarised as mean (SD), all other characteristics are n (%). Inverse probability weights used to correct for the random sampling of 'Vaccinated' patients.
```{r table2, include=FALSE}
read_rds(here::here("output", "tables", str_c("summary_table_09.rds"))) %>%
  my_flextable_1()
```
<!-- \pagebreak -->
Table 3. Characteristics of individuals in JCVI priority group 11 aged 30-39 years. 'Unvaccinated' = patients who did not receive a COVID vaccine within 12 weeks of becoming eligible; 'Vaccinated' otherwise. Age is summarised as mean (SD), all other characteristics are n (%). Inverse probability weights used to correct for the random sampling of patients.
```{r table3, include=FALSE}
read_rds(here::here("output", "tables", str_c("summary_table_11.rds"))) %>%
  my_flextable_1()
```

```{r or_table_function}
or_table <- function(g) {
  read_rds(file = here::here("output", "tables", glue("table_{g}_unadj.rds"))) %>%
  rename(Characteristic = characteristic,
         "OR (95% CI)" = OR) %>%
  my_flextable_2()
}
```


\pagebreak
Table 4. Odds ratios of being vaccinated within 12 weeks of eligibility date for each characteristic (JCVI priority group 2 aged 80+ years).
```{r table4, include=FALSE}
or_table("02")
```

\pagebreak
Table 5. Odds ratios of being vaccinated within 12 weeks of eligibility date for each characteristic (JCVI priority group 9 aged 50-54 years). 
```{r table5, include=TRUE}
or_table("09")
```

\pagebreak
Table 6. Odds ratios of being vaccinated within 12 weeks of eligibility date for each characteristic (JCVI priority group 11 aged 30-39 years).
```{r table6, include=TRUE}
or_table("11")
```

